\ttitle

### 2013-11-18 Appendices/AppendixA-summaries.tex
Add caption titles to tables
Restructure Chapter 5 graphs of data sets

Linear models are well studied, in particular for the problem of linear regression.
This can be solved by the \emph{least-squares} method and classification as discussed in Section~\ref{least-squares}, the \emph{perceptron} as explained in Section~\ref{perceptron}.
Linear regression with the \emph{support vector machine} is handled in Section~\ref{svm-explained} and used for probability density estimation in Section~\ref{linear-classifier-pdf}.
The kernel trick used for learning non-linear models is explained in Section~\ref{non-linear}.

@@

When the algorithm is completed, every $y_i\vectorsym{x}_i$ is added $\alpha_i$ times to the weight vector (every time it was misclassified).
Thus, the weight vector can be expressed as: $\vectorsym{w} = \sum_{i=i}^n \alpha_i y_i \vectorsym{x}_i$.
In other words: the weight vector is a linear combination of the training instances.
The dual form of the algorithm learns the instance weights $\alpha_i$ rather than the features weights $\vectorsym{w}_i$.
An instance $\vectorsym{x}$ is then classified as $\hat{y} = sign(\sum_{i=1}^n \alpha_i y_i \vectorsym{x}_i \cdot \vectorsym{x})$.
This means that during the training only the pairwise dot products of the data is needed; this results in the \emph{n}-by-\emph{n} Gram matrix $\matrixsym{G} = \matrixsym{X}\matrixsym{X}^T$.
This instance-based perspective will be further discussed in Section~\ref{svm-explained} about the support vector machine.

@@

This equation can be transformed with the Lagrange multipliers by adding the constraints to the minimization part with multipliers $\alpha_i$.
Taking the partial derivative with respect to $t$ and setting it to $0$, we find that for the optimal solution (threshold) $t$ we have $\sum_{i=1}^{n} \alpha_i y_i = 0$.
When we take the partial derivative with respect to $w\vectorsym{w}$ we see that the Lagrange multipliers define the weight vector as a linear combination of the training examples.
This partial derivative is $0$ for an optimal weight we get that $\vectorsym{w} = \sum_{i=1}^{n} \alpha_i y_i \vectorsym{x}_i$, \emph{which is the same expression as for the perceptron derived in Section~\ref{perceptron}}.
By plugging $\vectorsym{w}$ and $t$ back into the Lagrange equation, we can eliminate these and get the dual optimization problem entirely formulated in terms of the Lagrange multipliers:

@@

The second property enables powerful adaption for support vector machines to learn non-linear decision boundaries, as discussed in Section~\ref{non-linear}.

@@

\subsection{Change Point Detection In Time Series Data Using Support Vectors}
Paper by Fatih Camci \cite{camci2010change}
About segmentation with SVMs.
Will be main material for Section~\ref{sec:svm_in_change_detection} about SVMs.

@@

\subsubsection{Problem formulation}
[Not summarized here, useful for e.g. Section~\ref{statistical-framework}]

@@

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  1 & Start with $n$ observations and construct hyper-sphere \\
  2 & Add next observation $x_t$ and drop first one \\
  3 & Identify new hyper-sphere and its \emph{approximate radius} \\
  4 & if $x_t$ is outside hyper-sphere, mark $t$ as change points and continue from step 2 \\
  5 & calculate radius average of last $w$ hyper-planes \\
  6 & calculate radius ratio $\hbar$. If lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point \\
  7 & continue from step 2 \\
  \hline
\end{tabular}
\caption{Support Vector machine based Change Point Detection algorithm}
\label{tab:alg-svcdp}
\end{table}\end{center}

@@

The (expected) value of $D_k$ given a change in variance differs in the context.
If a smaller variance corresponds to the smaller portion of the series, then it will be harden to find the change point using $D_k$.
There is a masking effect when there are multiple change points in the series; the order of small, medium and large variances result in the value of $D_k$.
The iterative algorithm presented in this paper in Section~\ref{subsec:icss} is designed to lessen the masking effect.

@@

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  0 & Let $t_1 = 1$ \\
  1 & Calculate $D_k(\alpha[t_1 : T])$. Let $k^*(\alpha[t_1 : T])$ be the point at which $\text{max}_k \abs{D_k(\alpha[t_1 : T])}$. Let $D^*$ be the asymptotically critical value and $M$ the max value in the series segment (?). If $M > D^*$ then consider $k^*$ to be a change point. Else, there is no change point and the algorithm stops. \\
  2a & Repeat for the first part (up to the change point), until no more change points are found. \\
  2b & Repeat for the second part (from the change point forward), until no more change points are found. \\
  3 & When two or more change points are found; check for each $\alpha[j-1 : j+1]$ if there is indeed a change point ($j$). Repeat until the number of change points does not change and each new found change point is ``close'' enough to previous. \\
  \hline
\end{tabular}
\caption{Iterated Cumulative Sums of Squares Algorithm}
\label{tab:alg-icss}
\end{table}\end{center}

>>>>

Linear models are well studied, in particular for the problem of linear regression.
This can be solved by the \emph{least-squares} method and classification as discussed in \Cref{least-squares}, the \emph{perceptron} as explained in \Cref{perceptron}.
Linear regression with the \emph{support vector machine} is handled in \Cref{svm-explained} and used for probability density estimation in \Cref{linear-classifier-pdf}.
The kernel trick used for learning non-linear models is explained in \Cref{non-linear}.

@@

When the algorithm is completed, every $y_i\vectorsym{x}_i$ is added $\alpha_i$ times to the weight vector (every time it was misclassified).
Thus, the weight vector can be expressed as: $\vectorsym{w} = \sum_{i=i}^n \alpha_i y_i \vectorsym{x}_i$.
In other words: the weight vector is a linear combination of the training instances.
The dual form of the algorithm learns the instance weights $\alpha_i$ rather than the features weights $\vectorsym{w}_i$.
An instance $\vectorsym{x}$ is then classified as $\hat{y} = sign(\sum_{i=1}^n \alpha_i y_i \vectorsym{x}_i \cdot \vectorsym{x})$.
This means that during the training only the pairwise dot products of the data is needed; this results in the \emph{n}-by-\emph{n} Gram matrix $\matrixsym{G} = \matrixsym{X}\matrixsym{X}^T$.
This instance-based perspective will be further discussed in \Cref{svm-explained} about the support vector machine.

@@

This equation can be transformed with the Lagrange multipliers by adding the constraints to the minimization part with multipliers $\alpha_i$.
Taking the partial derivative with respect to $t$ and setting it to $0$, we find that for the optimal solution (threshold) $t$ we have $\sum_{i=1}^{n} \alpha_i y_i = 0$.
When we take the partial derivative with respect to $w\vectorsym{w}$ we see that the Lagrange multipliers define the weight vector as a linear combination of the training examples.
This partial derivative is $0$ for an optimal weight we get that $\vectorsym{w} = \sum_{i=1}^{n} \alpha_i y_i \vectorsym{x}_i$, \emph{which is the same expression as for the perceptron derived in \Cref{perceptron}}.
By plugging $\vectorsym{w}$ and $t$ back into the Lagrange equation, we can eliminate these and get the dual optimization problem entirely formulated in terms of the Lagrange multipliers:

@@

The second property enables powerful adaption for support vector machines to learn non-linear decision boundaries, as discussed in \Cref{non-linear}.

@@

\subsection{Change Point Detection In Time Series Data Using Support Vectors}
Paper by Fatih Camci \cite{camci2010change}
About segmentation with SVMs.
Will be main material for \Cref{sec:svm_in_change_detection} about SVMs.

@@

\subsubsection{Problem formulation}
[Not summarized here, useful for e.g. \Cref{statistical-framework}]

@@

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  1 & Start with $n$ observations and construct hyper-sphere \\
  2 & Add next observation $x_t$ and drop first one \\
  3 & Identify new hyper-sphere and its \emph{approximate radius} \\
  4 & if $x_t$ is outside hyper-sphere, mark $t$ as change points and continue from step 2 \\
  5 & calculate radius average of last $w$ hyper-planes \\
  6 & calculate radius ratio $\hbar$. If lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point \\
  7 & continue from step 2 \\
  \hline
\end{tabular}
\caption[\gls{svcpd} algorithm]{Support Vector machine based Change Point Detection algorithm}
\label{tab:alg-svcdp}
\end{table}\end{center}

@@

The (expected) value of $D_k$ given a change in variance differs in the context.
If a smaller variance corresponds to the smaller portion of the series, then it will be harden to find the change point using $D_k$.
There is a masking effect when there are multiple change points in the series; the order of small, medium and large variances result in the value of $D_k$.
The iterative algorithm presented in this paper in \Cref{subsec:icss} is designed to lessen the masking effect.

@@

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  0 & Let $t_1 = 1$ \\
  1 & Calculate $D_k(\alpha[t_1 : T])$. Let $k^*(\alpha[t_1 : T])$ be the point at which $\text{max}_k \abs{D_k(\alpha[t_1 : T])}$. Let $D^*$ be the asymptotically critical value and $M$ the max value in the series segment (?). If $M > D^*$ then consider $k^*$ to be a change point. Else, there is no change point and the algorithm stops. \\
  2a & Repeat for the first part (up to the change point), until no more change points are found. \\
  2b & Repeat for the second part (from the change point forward), until no more change points are found. \\
  3 & When two or more change points are found; check for each $\alpha[j-1 : j+1]$ if there is indeed a change point ($j$). Repeat until the number of change points does not change and each new found change point is ``close'' enough to previous. \\
  \hline
\end{tabular}
\caption[\gls{icss} algorithm]{Iterated Cumulative Sums of Squares Algorithm}
\label{tab:alg-icss}
\end{table}\end{center}

### 2013-11-18 Chapters/Chapter2.tex
Restructure Chapter 5 graphs of data sets

The widely used \gls{cusum} method by Basseville \etal \cite{basseville1993detection} follows this approach.
It originates from control methods for detection from benchmarks.
This method and some derivatiges are discussed and analyzed in Section~\ref{cusum}.

Many methods rely on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
The methods proposed by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the \glspl{pdf}, instead of estimating each \gls{pdf}.
This approach is discussed and analyzed in Section~\ref{density-ratio}.

The density-estimation methods rely on the log-likelihood ratio between \glspl{pdf}.
The method of Camci \cite{camci2010change} follows an other approach within the statistical framework, by using a \gls{svm}.
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using the kernel trick.
A change in the \gls{pdf} is represented by a change in the radius of this sphere.
Section~\ref{sec:svm_in_change_detection} discusses the \gls{svm}-methods.
\TODO{Put emphasis that this is the source of inspiration for the chosen method?}

% The final method under consideration, change detection via (intrinsic) dimensionality reduction, follows a different point of view.
% Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
% It uses the estimated underlying number of parameters of the time series as a model for change detection.
% Section~\ref{dim-reduction} discuses this method.

@@

\section{Overview}\label{sec:literature_review_overview}
As described in Chapter~\ref{Chapter1}, the focus of this research is the application of temporal segmentation to accelerometer data.
This is with the assumption that explicit temporal segmentation can aid the process of temporal classification.

@@

In the following section of this is chapter we begin with a review of current literature on temporal segmentation.
Many techniques of temporal segmentation rely in change detection algorithms.
In Section~\ref{sec:change_detection_methods} we will give an overview of those kind of algorithms.
An often encountered problem is the \emph{curse of dimensionality}.
To overcome this problem, we look at \gls{dr} methods in Section~\ref{sec:dimensionality_reduction}.
We end this chapter with a review on \gls{svm} based methods and algorithms.
This latter section relates the \gls{oc-svm} methods via \gls{dr} to temporal segmentation.

>>>>

The widely used \gls{cusum} method by Basseville \etal \cite{basseville1993detection} follows this approach.
It originates from control methods for detection from benchmarks.
This method and some derivatiges are discussed and analyzed in \Cref{sec:cusum}.

Many methods rely on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
The methods proposed by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the \glspl{pdf}, instead of estimating each \gls{pdf}.
This approach is discussed and analyzed in \Cref{sec:density-ratio}.

The density-estimation methods rely on the log-likelihood ratio between \glspl{pdf}.
The method of Camci \cite{camci2010change} follows an other approach within the statistical framework, by using a \gls{svm}.
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using the kernel trick.
A change in the \gls{pdf} is represented by a change in the radius of this sphere.
\Cref{sec:svm_in_change_detection} discusses the \gls{svm}-methods.
\TODO{Put emphasis that this is the source of inspiration for the chosen method?}

% The final method under consideration, change detection via (intrinsic) dimensionality reduction, follows a different point of view.
% Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
% It uses the estimated underlying number of parameters of the time series as a model for change detection.
% \Cref{dim-reduction} discuses this method.

@@

\section{Overview}\label{sec:literature_review_overview}
As described in \Cref{Chapter1}, the focus of this research is the application of temporal segmentation to accelerometer data.
This is with the assumption that explicit temporal segmentation can aid the process of temporal classification.

@@

In the following section of this is chapter we begin with a review of current literature on temporal segmentation.
Many techniques of temporal segmentation rely in change detection algorithms.
In \Cref{sec:change_detection_methods} we will give an overview of those kind of algorithms.
An often encountered problem is the \emph{curse of dimensionality}.
To overcome this problem, we look at \gls{dr} methods in \Cref{sec:dimensionality_reduction}.
We end this chapter with a review on \gls{svm} based methods and algorithms.
This latter section relates the \gls{oc-svm} methods via \gls{dr} to temporal segmentation.

### 2013-11-18 Chapters/Chapter2/svm.tex
WIP: Working on organization of Chapter 2
Restructure Chapter 5 graphs of data sets

The algorithms of \glspl{svm} has been applied to the problem of \gls{har}, as by Anguita \etal \cite{anguitahuman}.
In that research a multi-class classification problem is solved using \glspl{svm} and the One-Vs-All method.
The method exploits fixed-point arithmetic to create a hardware-friendly algorithm, which can be executed on a smartphone.\footnote{Smartphones have limited resources and thus require energy-efficient algorithms. In \cite{anguita2007hardware} a Hardware-Friendly \gls{svm} is introduced. It uses less memory, processor time and power consumption, with a loss of precision.}

@@

The inner workings of \glspl{oc-svm} are discussed in detail in Section~\ref{sec:one_class_svm}.

>>>>

The algorithms of \glspl{svm} has been applied to the problem of \gls{har}, as by Anguita \etal \cite{anguita2012human}.
In that research a multi-class classification problem is solved using \glspl{svm} and the One-Vs-All method.
The method exploits fixed-point arithmetic to create a hardware-friendly algorithm, which can be executed on a smartphone.\footnote{Smartphones have limited resources and thus require energy-efficient algorithms. In \cite{anguita2007hardware} a Hardware-Friendly \gls{svm} is introduced. It uses less memory, processor time and power consumption, with a loss of precision.}

@@

The inner workings of \glspl{oc-svm} are discussed in detail in \Cref{sec:one_class_svm}.

### 2013-11-18 Chapters/Chapter3.tex
Restructure Chapter 5 graphs of data sets

This chapter discusses the concepts and algorithms that will be used as a basis for the proposed method, as discussed in Chapter~\ref{Chapter4}.
The first sections formulates the problem of change detection and relates it to outlier and novelty detection.
It transforms the traditional problem to change detection for times series data.
In Section~\ref{sec:one_class_classification} the problem of \acrlong{occ} is discussed and shows a number of implementations.
Two \acrlong{svm}-based methods, \gls{nu-svm} and \gls{svdd}, are further disussed in Section~\ref{sec:one_class_svm}.
For the application to the problem of \acrlong{har}, the characteristics of the collected sensor data is discussed in~\ref{sec:sensor_data_characteristics}.
Finally a theoretic set of quality metrics is discussed in Section~\ref{sec:quality_metrics}.

>>>>

This chapter discusses the concepts and algorithms that will be used as a basis for the proposed method, as discussed in \Cref{Chapter4}.
The first sections formulates the problem of change detection and relates it to outlier and novelty detection.
It transforms the traditional problem to change detection for times series data.
In \Cref{sec:one_class_classification} the problem of \acrlong{occ} is discussed and shows a number of implementations.
Two \acrlong{svm}-based methods, \gls{nu-svm} and \gls{svdd}, are further disussed in \Cref{sec:one_class_svm}.
For the application to the problem of \acrlong{har}, the characteristics of the collected sensor data is discussed in~\ref{sec:sensor_data_characteristics}.
Finally a theoretic set of quality metrics is discussed in \Cref{sec:quality_metrics}.

### 2013-11-18 Chapters/Chapter3/one_class_classification.tex
Restructure Chapter 5 graphs of data sets

The problem of \gls{occ} is closely related to the (traditional) two-class classification situation\footnote{Two-class problems are considered as to be the basic problem, since multi-class classification problems can be decomposed into multiple two-class problems \cite{fukunaga1990introduction}.}.
In the case of traditional classification algorithms, the problem is to classify an unknown object to one of the pre-defined categories.
Every object $i$ is represented as a vector $\vectorsym{x}_i = (x_{i,1},\dots,x_{i,d}), x_{i,j} \in \mathbb{R}$ with $d$ real-valued measurements.
Using this notation, an object $\vectorsym{x}_i$ thus represents one point in a feature space: $\vectorsym{x}_i \in \mathcal{X} = \mathbb{R}^d$.
The two classes of objects, $\omega_1$ and $\omega_2$, are labeled $-1$ and $+1$ respectively.
The objects with a label $y_i \in \{-1, +1\}$ attached are in the training set $\mathcal{X}^{tr}$ (note that it can be both positive and negative example objects).
This problem is solved by determining a decision boundary in the feature space of the data objects and label the new data object based on the location relative to this boundary.
This is expressed by the decision function $y = f(\vectorsym{x})$:
\begin{equation}\label{eq:decision_function_classification}
  f: \mathbb{R}^d \rightarrow \{-1, +1\}
\end{equation}
In case of the \gls{occ} problem, only one class (often referred as the target class, or positive examples) of training data is used to create a decision boundary.
The goal is to determine whether a new data object belongs to the target class or to the unknown class and thus is an outlier.
One could argue that this problem is equal to the traditional two-class problem by considering all other classes as negative examples, although there are important differences.
In pure \gls{occ} problems there are no negative example objects available.
This could be because the acquisition of these examples is very expensive, or because there are only examples of the `normal' state of the system and the goal is to detect `abnormal' states.
Since the algorithm's goal is to differentiate between normal and abnormal objects (relative to the training objects), \gls{occ} is often called outlier, novelty or anomaly detection, depending on the origin of the problem to which the algorithm is applied\footnote{The term \acrlong{occ} originates from Moya \etal \cite{moya1993one}.}.
The difference between two and one-class classification and the consequence for outlier objects is illustrated in Figure~\ref{fig:two-vs-one-classification}.
In the two-class classification problem the object \textbf{o} will be member of the \textbf{-1} class whilst the \gls{occ} problem will label it as an outlier.
In \cite{tax2001one} a more detailed analysis of the \gls{occ} is given.

@@

\subsection{One-Class Classification methods}\label{subsec:occ-methods}
The methods and algorithms used for the \gls{occ}-problem can be organized into three categories \cite{tax2001one,noumir2012simple}, visually represented in Figure~\ref{fig:occ-methods}.
The first category consists of methods that estimate the density of the training data and set a threshold on this density.
Among those are Gaussian models, \glspl{gmm} and Parzen density estimators.
In order to get good generalization results with these methods, the dimensionality of the data and the complexity of the density need to be restricted.
This can cause a large bias on the data.
When a good probability model is assumed, these methods work very well, since when one threshold is optimized, a minimum volume is automatically found for the given probability density model \cite{tax2001one}.

Boundary methods are based on Vapnik's principle\footnote{With a limited amount of data available, on should avoid solving a more general problem as an intermediate step to solve the original problem \cite{vapnik1998statistical}.} which imply in this case that estimating the complete data density for a \gls{occ} may be too complex, in case one is only interested in the closed boundary.
Examples of methods that focus on the boundary (a direct threshold) of the training data distribution are K-centers, Nearest-neighborhood and \gls{svdd} or a combination of those methods \cite{hempstalk2008one}.
Especially the latter has a strong bias towards minimal volume solutions.
These type of methods are sensitive to scaling of features, since they rely on a well-defined distance measure.
The number of objects that is required is smaller than in the case of density methods.
The boundary method \gls{svdd}, constructed by Tax and which has shown good performance \cite{khan2010survey}, will be further discussed in Section~\ref{subsec:oc-svm-svdd}.

@@

In \cite{khan2010survey,noumir2012simple} an overview of applications for \gls{occ}-algorithms, and explictly for \gls{svm}-based methods (such as \gls{svdd} and \gls{nu-svm}), is given.
It shows succesful applications for, amonst others, problems in the field of Handwritten Digit Recognition, Face Recognition Applications, Spam Detection and Anomaly Detection \cite{li2003improving,perdisci2006using}.
As discussed in Section~\ref{sec:change_detection_time_series}, this can be used for change detection in time series data.

>>>>

The problem of \gls{occ} is closely related to the (traditional) two-class classification situation\footnote{Two-class problems are considered as to be the basic problem, since multi-class classification problems can be decomposed into multiple two-class problems \cite{fukunaga1990introduction}.}.
In the case of traditional classification algorithms, the problem is to classify an unknown object to one of the pre-defined categories.
Every object $i$ is represented as a vector $\vectorsym{x}_i = (x_{i,1},\dots,x_{i,d}), x_{i,j} \in \mathbb{R}$ with $d$ real-valued measurements.
Using this notation, an object $\vectorsym{x}_i$ thus represents one point in a feature space: $\vectorsym{x}_i \in \mathcal{X} = \mathbb{R}^d$.
The two classes of objects, $\omega_1$ and $\omega_2$, are labeled $-1$ and $+1$ respectively.
The objects with a label $y_i \in \{-1, +1\}$ attached are in the training set $\mathcal{X}^{tr}$ (note that it can be both positive and negative example objects).
This problem is solved by determining a decision boundary in the feature space of the data objects and label the new data object based on the location relative to this boundary.
This is expressed by the decision function $y = f(\vectorsym{x})$:
\begin{equation}\label{eq:decision_function_classification}
  f: \mathbb{R}^d \rightarrow \{-1, +1\}
\end{equation}
In case of the \gls{occ} problem, only one class (often referred as the target class, or positive examples) of training data is used to create a decision boundary.
The goal is to determine whether a new data object belongs to the target class or to the unknown class and thus is an outlier.
One could argue that this problem is equal to the traditional two-class problem by considering all other classes as negative examples, although there are important differences.
In pure \gls{occ} problems there are no negative example objects available.
This could be because the acquisition of these examples is very expensive, or because there are only examples of the `normal' state of the system and the goal is to detect `abnormal' states.
Since the algorithm's goal is to differentiate between normal and abnormal objects (relative to the training objects), \gls{occ} is often called outlier, novelty or anomaly detection, depending on the origin of the problem to which the algorithm is applied\footnote{The term \acrlong{occ} originates from Moya \etal \cite{moya1993one}.}.
The difference between two and one-class classification and the consequence for outlier objects is illustrated in \Cref{fig:two-vs-one-classification}.
In the two-class classification problem the object \textbf{o} will be member of the \textbf{-1} class whilst the \gls{occ} problem will label it as an outlier.
In \cite{tax2001one} a more detailed analysis of the \gls{occ} is given.

@@

\subsection{One-Class Classification methods}\label{subsec:occ-methods}
The methods and algorithms used for the \gls{occ}-problem can be organized into three categories \cite{tax2001one,noumir2012simple}, visually represented in \Cref{fig:occ-methods}.
The first category consists of methods that estimate the density of the training data and set a threshold on this density.
Among those are Gaussian models, \glspl{gmm} and Parzen density estimators.
In order to get good generalization results with these methods, the dimensionality of the data and the complexity of the density need to be restricted.
This can cause a large bias on the data.
When a good probability model is assumed, these methods work very well, since when one threshold is optimized, a minimum volume is automatically found for the given probability density model \cite{tax2001one}.

Boundary methods are based on Vapnik's principle\footnote{With a limited amount of data available, on should avoid solving a more general problem as an intermediate step to solve the original problem \cite{vapnik1998statistical}.} which imply in this case that estimating the complete data density for a \gls{occ} may be too complex, in case one is only interested in the closed boundary.
Examples of methods that focus on the boundary (a direct threshold) of the training data distribution are K-centers, Nearest-neighborhood and \gls{svdd} or a combination of those methods \cite{hempstalk2008one}.
Especially the latter has a strong bias towards minimal volume solutions.
These type of methods are sensitive to scaling of features, since they rely on a well-defined distance measure.
The number of objects that is required is smaller than in the case of density methods.
The boundary method \gls{svdd}, constructed by Tax and which has shown good performance \cite{khan2010survey}, will be further discussed in \Cref{subsec:oc-svm-svdd}.

@@

In \cite{khan2010survey,noumir2012simple} an overview of applications for \gls{occ}-algorithms, and explictly for \gls{svm}-based methods (such as \gls{svdd} and \gls{nu-svm}), is given.
It shows succesful applications for, amonst others, problems in the field of Handwritten Digit Recognition, Face Recognition Applications, Spam Detection and Anomaly Detection \cite{li2003improving,perdisci2006using}.
As discussed in \Cref{sec:change_detection_time_series}, this can be used for change detection in time series data.
